Refunctionalization of Abstract Abstract Machines

### 2020-12-30 paper/paper.tex
misc

But as mentioned above, defunctionalization and refunctionalization are more general concepts,
with a wide range of uses. For example, \citet{Danvy:2001:DW:773184.773202} showed that
defunctionalization is dual to Church encoding, and further case studies where known
higher-order and first-order implementations can be related through defunctionalization
and refunctionalization include backtracking algorithms (e.g., regular expression matcher),
Dyck word recognizer, Dijkstra's shunting-yard algorithm, and even Quicksort
\cite{Danvy:2006:RW:2171265.2171268, DANVY2009534, Danvy:2001:DW:773184.773202}. \\

>>>>

But as mentioned above, defunctionalization and refunctionalization are more general concepts,
with a wide range of uses. For example, \citet{Danvy:2001:DW:773184.773202} showed that
defunctionalization is dual to Church encoding, and further case studies show that known
higher-order and first-order implementations can be related through defunctionalization
and refunctionalization, including backtracking algorithms (e.g., regular expression matcher),
Dyck word recognizer, Dijkstra's shunting-yard algorithm, and even Quicksort
\cite{Danvy:2006:RW:2171265.2171268, DANVY2009534, Danvy:2001:DW:773184.773202}. \\
